\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
tidied intro

\begin{abstract}
\spacingset{1.45}
  A geometric interpretation is developed for so-called \emph{reconciliation} methodologies used to forecast time series that adhere to known linear constraints. In particular, a general framework is established nesting many existing popular reconciliation methods within the class of \emph{projections}. This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecast accuracy with respect to a specific class of loss functions. The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts provided the initial Approaches for dealing with biased base forecasts are proposed.  The implications of all theoretical results are demonstrated in an extensive empirical study on Australian tourism flows. The method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.

>>>>

\begin{abstract}
\spacingset{1.45}
  A geometric interpretation is developed for so-called \emph{reconciliation} methodologies used to forecast time series that adhere to known linear constraints. In particular, a general framework is established nesting many existing popular reconciliation methods within the class of \emph{projections}. This interpretation facilitates the derivation of novel theoretical results. First, reconciliation via projection is guaranteed to improve forecast accuracy with respect to a class of loss functions based on a generalised distance metric. Second, the MinT method minimises expected loss for this same class of loss functions.  The geometric interpretation is further used to provide a new proof that forecast reconciliation using projections results in unbiased forecasts provided the initial base forecasts are also unbiased.  Approaches for dealing with biased base forecasts are proposed and evaluated in an extensive empirical study on Australian tourism flows. The method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.  The empirical study also sheds light on the theoretical results of the paper.
